A Comparison of Graph Processing Systems

### 2020-09-18 documentation/paper/sections/overview/galois.tex
Preliminaries section description + Galois writeup improvements

%!TEX root=../../main.tex
%TODO add bibliography for origGalois and cite it here
Galois \cite{origGalois} is a general purpose library designed for parallel programming. The system reduces the complexity of writing parallel applications by providing implicitly parallel (unordered or partially ordered) set iterators. These iterators perform operations optimistically, detect arising conflicts and resolve these by invoking inverse methods accordingly. The tasks in the sets can be ordered, the tasks may be executed out of order, but the conflict resolution will ensure semantic equivalence to sequential strictly ordered execution.

@@

The graph analysis subsystem of Galois \cite{Galois} provides a library of scalable data structures and a topology aware priority scheduler, including optimizations for distributed execution. The scheduler splits the tasks into bags according to a specified partial order, which in turn provide the cores with chunks of tasks. A global map manages the various bags. Every thread keeps a lazy cache of a portion of the global map, in order to reduce the strain on the global map. Galois includes applications for many graph analytics problems, among these are SSSP, BFS and pagerank. For most of these applications Galois offers several different algorithms to perform these analytics problems and many options e.g. the amount of threads used or policies for splitting the graph. All of these applications can be executed in shared memory systems and, due to the Gluon integration, with a few modifications in a distributed environment

>>>>

%!TEX root=../../main.tex
%TODO add bibliography for origGalois and cite it here
Galois \cite{origGalois} is a general purpose library designed for parallel programming. The system reduces the complexity of writing parallel applications by providing implicitly parallel (unordered or partially ordered) set iterators. These iterators perform operations optimistically, detect arising conflicts and resolve them by invoking inverse methods accordingly. The tasks can be ordered, the ordering ensures a sequential strictly ordered semantic. Ordered tasks may still be executed out of order without affecting the ordered semantic due to the conflict resolution.

@@

The graph analysis subsystem of Galois \cite{Galois} provides a library of scalable data structures and a topology aware priority scheduler, including optimizations for distributed execution. The scheduler splits the tasks into bags according to a specified partial order, which in turn provide the cores with chunks of tasks. A global map manages the various bags. Every thread keeps a lazy cache of a portion of the global map, in order to reduce the strain on the global map. Galois includes applications for many graph analytics problems, among these are SSSP, BFS and pagerank. For most of these applications Galois offers several different algorithms to perform these analytics problems and many options e.g. the amount of threads used or policies for splitting the graph. All of these applications can be executed in shared memory systems and, due to the Gluon integration, with a few modifications in a distributed environment \cite{vertGalois}.

%For graph analytics purposes a topology aware work stealing scheduler, a priority scheduler and a library of scalable data structures have been implemented. Galois includes applications for many graph analytics problems, among these are Single-Source Shorthest-Paths (SSSP), Breath-First Search (BFS) and PageRank (PR). For most of these applications Galois offers several different algorithms to perform these analytics problems and many setting options like the amount of threads used or policies for splitting the graph. All of these applications can be executed in shared memory systems and, due to the Gluon integration, with a few modifications in a distributed environment.

### 2020-09-18 documentation/paper/sections/preliminiaries.tex
citation for the congest model
Preliminaries section description + Galois writeup improvements

\section{Preliminaries}
\todo{Section beschreiben}

>>>>

\section{Preliminaries}
\todo{Section beschreiben}
This section briefly explain the concepts and applications necessary, but not directly related to our work. 
Initialy graphs and paths are defined, followed by explanations for various graph analysis applications.
Afterwards a few models for compution on graphs or large data sets in general are explained as well as hugepages.
